Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-11-13 manuscript/manuscript.tex
BH's suggestion

Besides a detailed demonstration of the above, Notebook (06) demonstrates how to compute J-couplings and dynamic fingerprints from MSMs.

@@

More details on how to model complex systems with the techniques presented here are described, e.g., by~\cite{plattner_protein_2015,plattner_complete_2017}.
We further demonstrate the symptoms of difficult data situations and how to deal with them in Notebook (08).

>>>>

In addition to a detailed demonstration of the above, Notebook (06) demonstrates how to compute J-couplings and dynamic fingerprints from MSMs.

@@

More details on how to model complex systems with the techniques presented here are described, e.g., by~\cite{plattner_protein_2015,plattner_complete_2017}.
We further examine some symptoms that may indicate problematic or difficult datasets, and demonstrate how to deal with them in Notebook (08).
